TEXT

### 2020-09-09 Article/ici_submm_cloudcorr.tex
added references.bib and renamed Article.tex to ici_submm_cloudcorr.tex
new additions to the article; backing up

\introduction  %% \introduction[modified heading if necessary]
TEXT
\section{Introduction}

@@

\subsection{ICI}
%
%t
\begin{table*}[t]
	\label{tab:QRNN_models}	
	\caption{TEXT}
	\begin{tabular}{lrrrr}
		\tophline
		Channel & Frequency 	& Bandwidth  	&NE$\Delta$T	&Polarisation\\
		\middlehline
		I1V&	183.31$\pm$7.00    & 2.0 			& 0.8 		& V\\
		I2V&	183.31$\pm$3.40    & 1.5 			& 0.8 		& V\\
		I3V&	183.31$\pm$2.00    & 1.5 			& 0.8 		& V\\
		I4V&	243.20$\pm$2.50    & 3.0 			& 0.7 		& V\\
		I4H&	243.20$\pm$2.50    & 3.0 			& 0.7 		& H\\
		I5V&	325.15$\pm$9.50    & 3.0 			& 1.2 		& V\\
		I6V&	325.15$\pm$3.50    & 2.4 			& 1.3 		& V\\
		I6V&	325.15$\pm$1.50    & 1.6 			& 1.5 		& V\\
		I8V&	448.00$\pm$7.20    & 3.0 			& 1.4 		& V\\
		I9V&	448.00$\pm$3.00    & 2.0 			& 1.6 		& V\\
		I10V&	448.00$\pm$1.40    & 1.2 			& 2.0 		& V\\
		I11V&	664.00$\pm$4.20    & 5.0 			& 1.6 		& V\\
		I11H&	664.00$\pm$4.20    & 5.0 			& 1.6 		& H\\		
		\bottomhline
	\end{tabular}
	\begin{tabular}{lrrrr}
		\tophline
		Channel & Frequency 	& Bandwidth  	&NE$\Delta$T	&Polarisation\\
		\middlehline
		MWI-14&	183.31$\pm$7.00    & 2.0 			& 1.3 		& V\\
		MWI-15&	183.31$\pm$6.10    & 1.5 			& 1.2 		& V\\
		MWI-16&	183.31$\pm$4.90    & 1.5 			& 1.2 		& V\\
		MWI-16&	183.31$\pm$3.40    & 1.5 			& 1.2 		& V\\
		MWI-16&	183.31$\pm$2.00    & 1.5 			& 1.3 		& V\\	
		\bottomhline
	\end{tabular}
	\belowtable{} % Table Footnotes
\end{table*}
Ice Cloud Imager (ICI) is a new EPS-SG (EUMETSAT Polar System - Second Generation) sensor that will observe  Earth using submillimeter-wave (sub-mm) frequency range. The main objective of ICI is measure ice cloud properties and improve the representation of clouds in regional and global models. ICI is a conically scanning millimetre/sub-millimetre radiometer which will measure 13 frequencies from 183 GHz up to 664 GHz. Channels with centre frequencies 183.31, 325.15 and 448.0\,GHz are centered on water vapor absorption lines, and measure vertical polarization. While other channels around 243.0 and 664.0\,GHz are ``window channels'' and receive both vertical and horizontal polarization. 
In addition to ICI, the EPS-SG satellite will also have Microwave Imager (MWI) onboard. MWI will measure frequencies from 18.7 GHz up to 183\,GHz and provide data continuity to the existing microwave imager measurements. The common 183\,GHz channels among the two instruments shall allow cross-calibration between the two instruments. The channel configurations for ICI and MWI (only 183\,GHz) are provided in Table~\ref{tab:ICI_MWI_configuration}.

\subsection{ICI simulations}
%
**** Some parts copied directly from AWS report *****

@@

\section{Cloud correction in ICI 183 GHz channels}
%
\subsection{Training data}
%
Out of the 200\,000 ICI channel simulations, 150\,000 cases are randomly picked to form the training set. The rest are used for testing. In the training set, 90\% of the data is randomly selected to form the training set, while the other 10\% form the \textit{testing-during-training} database. ARTS simulations are noise free, so to incorporate the satellite measurement uncertainties, gaussian noise is added to the input training data according to the channel NE$\Delta$T. The target training data is kept noise free. In order to build a robust learning network, random noise is added to the inputs at each training iteration. This exposes the model to a different datasets during the entire training process and avoids the memorisation of training samples. The input data is also normalized with mean and standard deviation.

\subsection{Training}
%
%t
\begin{table}[t]
\label{tab:QRNN_models}	
\caption{TEXT}
\begin{tabular}{lll}
\tophline
QRNN model & Training inputs & Target \\
\middlehline
QRNN-simple & I1V, I5V, I6V, I7V, I8V, I9V, I10V, I11V & I1V\\
			& I2V, I5V, I6V, I7V, I8V, I9V, I10V, I11V & I2V\\
			& I3V, I5V, I6V, I7V, I8V, I9V, I10V, I11V & I3V\\
QRNN-all    & I1V, I2V, I3V, I5V, I6V, I7V, I8V, I9V, I10V, I11V & I1V\\	
			& I1V, I2V, I3V, I5V, I6V, I7V, I8V, I9V, I10V, I11V & I2V\\	
			& I1V, I2V, I3V, I5V, I6V, I7V, I8V, I9V, I10V, I11V & I3V\\
QRNN-mwi	& MWI-15, I5V, I6V, I7V, I8V, I9V, I10V, I11V & MWI-15\\	
			& MWI-16, I5V, I6V, I7V, I8V, I9V, I10V, I11V & MWI-16\\			
\bottomhline
\end{tabular}
\belowtable{} % Table Footnotes
\end{table}
To investigate the performance of training inputs, two QRNN models with different set of training inputs are analysed. In both models, the training set combines data from 183\,GHz, 325 GHz, 448\,GHz and 664\,GHz to predict cloud corrected observations for the target 183\,GHz channel.

In the first model, the training set includes the target 183\,GHz channel and the sub-mm channels. For example, to train for channel I1V, the input channels are I1V, I5V , I6V, I7V, I8V, I9V, I10V, I11V. A separate QRNN model is trained for each of the 183\,GHz channels. We shall refer this QRNN model as ``QRNN-simple''.

In the second QRNN model, we sugest to use all three 183\,GHz channels concurrently  with the other sub-mm channels. In this case, although the input training parameters are same for all channels, QRNN needs to be trained separately each 183\,GHz channel. Further in text, we refer this model as ``QRNN-all''. Table~\ref{tab:QRNN_models} summarises the two QRNN models.

As described in section \ref{model_selection}, a grid search was implemented to select the best performing hyperparamters. The mean quantile loss and CRPS for different layer width and hidden layer configurations are shown in Fig\ref{fig:model_selection}. The results are for QRNN-simple with I3V as target channel. Increasing the complexity of the network by increasing the layer-width and depth has a positive impact on performance. However for four hidden layers, increasing the number of neurons beyond 128 has no significant impact on the performance. On basis of these results, a neural network with four hidden layers and 128 neurons in each layer was selected for QRNN-simple.

For the optimising the training paramters, a customised  learning rate scheduler was implemented. The initial learning rate was reset after a certain number of epochs.  We started the training process with a initial learning rate of 0.1, and decreased it by a factor of 10 after 100 epochs. The best neural network performance was obtained when the network was trained three times with a new initial learning rate. For each training  if the validation loss remained unchanged till 6 training epochs, the learning rate was reduced by a factor of 2. We did not optimise the type of activation function and batch size. Rectified Linear Unit (ReLU) was used as the activation function  and the batch size was set to 128 samples for all QRNN models. 
For QRNN-all a grid search (results not shown) over width and depth and learning rates resulted in similar performance, and an identical neural network was selected.

\begin{figure}[t]
	\centering
	\includegraphics[height=57mm]{Figures/CRPS.png} 
	\includegraphics[height=57mm]{Figures/quantile_loss.png}
	\caption{}
	\label{fig:}	
\end{figure}

\subsection{Prediction results}
%
%f 
\begin{figure}[t]
	\includegraphics[height=57mm]{Figures/PDF_I1V_single.png} 
	\includegraphics[height=57mm]{Figures/PDF_I2V_single.png}
	\includegraphics[height=57mm]{Figures/PDF_I3V_single.png} 
	\caption{PDF}
	\label{fig:PDF_predictions}	
\end{figure}
%f 
\begin{figure}[t]
	\includegraphics[height=57mm]{Figures/ICI_I1V_single.png} 
	\includegraphics[height=57mm]{Figures/ICI_I2V_single.png}
	\includegraphics[height=57mm]{Figures/ICI_I3V_single.png} 
	\caption{Error distributions}
	\label{fig:error_distributions}	
\end{figure}

%t
\begin{table}[t]
	\caption{I1V}
	\label{tab:I1V_statistics}
	\begin{tabular}{lrrrrrr}
		\tophline
		&&& \multicolumn{2}{c}{QRNN-simple} & \multicolumn{2}{c}{QRNN-all}\\
		&   noise &   uncorrected &   corrected(all) &   corrected(filtered) & corrected(all) &   corrected(filtered) \\
		\middlehline
		bias     &   -0.00 &         -1.90 &           -0.03 &                 0.00 & -0.01 &                 0.01 \\
		mae      &    0.64 &          2.35 &            0.69 &                 0.60 & 0.66 &                 0.58\\
		std      &    0.80 &          8.92 &            1.05 &                 0.78 &  0.96 &                 0.75\\
		skewness &   -0.01 &         -7.99 &           -1.24 &                -0.44 & -0.39 &                -0.32\\
		rejected &    	 - &          - &            - &                 6.40 & - &                 6.42 \\
		\bottomhline
	\end{tabular}
	\belowtable{} % Table Footnotes
\end{table}
%t
\begin{table}[t]
	\caption{I2V}
	\label{tab:I2V_statistics}
	\begin{tabular}{lrrrrrr}
		\tophline
		&&& \multicolumn{2}{c}{QRNN-simple} & \multicolumn{2}{c}{QRNN-all}\\
		&   noise &   uncorrected &   corrected(all) &   corrected(filtered) & corrected(all) &   corrected(filtered) \\
		\middlehline
		bias     &   -0.00 &         -1.05 &            0.02 &                 0.03&  0.02&   0.03\\
		mae      &    0.64 &          1.54 &            0.56 &                 0.50&  0.46&   0.42\\
		std      &    0.80 &          5.98 &            0.86 &                 0.64&  0.70&   0.53\\
		skewness &    0.02 &        -10.64 &           -2.25 &                -0.22& -1.67&  -0.25\\
		rejected &    - &          - &            - &                 3.70&  - &   3.67\\
		\bottomhline
	\end{tabular}
	\belowtable{} % Table Footnotes
\end{table}

%t
\begin{table}[t]
	\caption{I3V}
	\label{tab:I3V_statistics}
	\begin{tabular}{lrrrrrr}
		\tophline
		&&& \multicolumn{2}{c}{QRNN-simple} & \multicolumn{2}{c}{QRNN-all}\\
		&   noise &   uncorrected &   corrected(all) &   corrected(filtered) & corrected(all) &   corrected(filtered) \\
		\middlehline
		bias     &   0.00 &         -0.63 &            0.02 &                 0.02& 0.04 &                 0.04 \\
		mae      &    0.64 &          1.14 &            0.54 &                 0.50&0.48 &                 0.44 \\
		std      &    0.80 &          4.26 &            0.80 &                 0.64&0.71 &                 0.56 \\
		skewness &   0.00 &        -13.26 &           -1.40 &                -0.16&-1.41 &                -0.11 \\
		rejected &    - &          - &           - &                 2.18&- &                 2.18 \\
		\bottomhline
	\end{tabular}
	\belowtable{} % Table Footnotes
\end{table}
QRNN predictions are estimates of the posterior distribution over different quantiles: $x_{\tau}$, for median, $\pm 1\sigma$, $\pm 2 \sigma$ and  $\pm 3 \sigma$ ($\tau$ = 0.002, 0.03, 0.16, 0.5, 0.84, 0.97, 0.998). The median of the posterior distribution is assumed to be the best estimate for the predicted clear-sky value. The prediction error is calculated as the deviation to the corresponding noise-free clear-sky value. We calculate the mean bias, mean absolute error and standard deviation of the errors. The asymmetry of the distributions around their mean is also calculated through the measure of skewness. In the following sections, we describe the performance of the two QRNN models.

The distributions of the predicted clear-sky values and the clear-sky simulations from QRNN-single are shown in Fig~\ref{fig:PDF_predictions}. The three figures correspond to channels: I1V, I2V and I3V. These results show that the clear-sky values predicted by QRNN-single have a very good match for the peak of the distributions, but a slight mismatch is evident towards the tails, where QRNN seems to predict slightly colder/warmer TBs.

Fig~\ref{fig:error_distributions} shows the error distributions of the uncorrected measurements and predicted clear-sky TBs for all three channels. Distribution of noise is also plotted for reference.  The error metrics corresponding to these results are provided in Table~\ref{tab:I1V_statistics} - Table~\ref{tab:I3V_statistics}. Without any cloud impact, the error distributions should follow a Gaussian distribution, however the presence of clouds leads to a TB reduction, and introduces a high negative bias. Among the three channels, I1V has the highest cloud impact and I3V has the least. The bias in I1V measurements is -1.89\,K compared to only -0.55\,K in I3V. After correction, the cloud impact is reduced and the resulting error distributions are symmetric with low bias. The predictions and the observations have a good agreement for the main peak of the distribution, albeit the prediction errors have a sharper peak and a larger spread. The larger spread indicates few cases which are under-/over corrected. If all the cases with correction greater than 15\,K are excluded, only a fraction of the total cases are removed but the  the variability in predictions errors reduces significantly. This indicates low accuracy of QRNN predictions for cases with high cloud impact.

Compared to channel I1V, the performance of QRNN model is slighly better for I2V and I3V.

The error metrics from QRNN-all are also shown in the last columns of Table~\ref{tab:I1V_statistics} - Table~\ref{tab:I3V_statistics}. As expected, using additional 183\,GHz channels improves the accuracy of the predictions slightly.

**** add QRNN-all results ****

\subsection{Uncertainty quantification}
%
%f 
\begin{figure}[t]
	\includegraphics[height=57mm]{Figures/scatter_uncertainty_single_I1V.png} 
	\includegraphics[height=57mm]{Figures/scatter_uncertainty_single_I2V.png}
	\includegraphics[height=57mm]{Figures/scatter_uncertainty_single_I3V.png} \\
	\includegraphics[height=57mm]{Figures/Frequency_uncertainty_bins_I1V_single.png} 
	\includegraphics[height=57mm]{Figures/Frequency_uncertainty_bins_I2V_single.png}
	\includegraphics[height=57mm]{Figures/Frequency_uncertainty_bins_I3V_single.png}
	\\	
	\caption{}
	\label{fig:error_distributions}	
\end{figure}
The biggest advantage of using QRNN is estimation of case-specific uncertainties. The quantiles can be used to construct a probability distribution of the
predictions in contrast to other correction approaches which give out only point estimates. In all QRNN models presented in this article, we estimate the conditional
quantiles for median, $\pm 1\sigma$, $\pm 2\sigma$, and $\pm 3\sigma$. The
predictions for each quantile are used to construct the confidence intervals.
The confidence interval for each point estimate quantifies its uncertainty. For example, the predicted quantiles for $\pm 2 \sigma$ implies that there is  94\% probability that the true value will lie between the range.

Fig~\ref{fig:uncertainty_scatter} shows the scatter plot between the error and uncertainty. The error distributions for all three channels are centered around zero, however the uncertainty in predictions for I1V and I2V are higher than I3V. An increase in the spread with increasing uncertainty is evident in all three. As the errors increase, the spread is mostly symmetric around x-axis but for high uncertainty values, negative errors occur more frequently. This suggests that predictions for cases high cloud impact are associated with high uncertainty. The lower panel in the same figure, shows the errors when plotted as distributions over different uncertainty bins. Apart from few individual variations, all three channels follow the trend of increasing uncertainty with decreasing accuracy, suggesting that QRNN is successful in providing well calibrated probabilistic predictions of the posterior distribution.

%Fig~\ref{fig:uncertainty_estimate} shows the prediction uncertainties for randomly chosen 2000 cases. A large spread in the plot indicates a high case-to-case variability of the uncertainty.

%To inspect if the predictions follow a normal distribution, we evaluate the length of confidence intervals from the median. Figure~\ref{fig:prediction_uncertainty} shows the prediction uncertainty in AWS-34 (four channel option). The uncertainty with respect to the median for 1000 randomly selected cases is shown. The red line represents the uncertainty in a hypothetical Gaussian distribution of $270\pm0.62$\,K. If the underlying distribution is Gaussian, the prediction uncertainty should be symmetric around the median, and the uncertainties should be equally spaced for $1\sigma$, $2\sigma$ and so on. The predictions from our QRNN model seem to be symmetric around the median for the 94\% confidence interval ($\pm 2 \sigma$). The figure also shows that the uncertainties for all 1000 random cases are concentrated along a narrow width, thus suggesting that the case to case variability of the uncertainty is low. A similar uncertainty quantification for other 183\,GHz channels also gives similar results.

%f
%\begin{figure}[t]
%\includegraphics[height=57mm]{Figures/uncertainty_single_I1V.png} 
%\includegraphics[height=57mm]{Figures/uncertainty_single_I2V.png}
%\includegraphics[height=57mm]{Figures/uncertainty_single_I3V.png} 
%\caption{}
%\label{fig:}
%\end{figure}

\section{Special case of using only 325\,GHz for cloud correction}

\subsection{Data}
24 monochromatic frequencies were used so that each channel could be represented
with sufficient accuracy. The simulations were generated for sensor viewing angles from
$0^{\circ}$ to $45^{\circ}$, but all the results described here are based on nadir viewing angle.

\subsection{Training}

\subsection{Prediction results}

\conclusions  %% \conclusions[modified heading if necessary]

>>>>

\introduction  %% \introduction[modified heading if necessary]

@@

\subsection{Ice Cloud Imager}
%
%t
\begin{table*}[t]
	\label{tab:ICI_MWI_channels}	
	\caption{Specifications of ICI and MWI channels. For MWI only 183\,GHz channels are shown.}
	\begin{tabular}{lrrrr}
		\tophline
		Channel & Frequency 	& Bandwidth  	&NE$\Delta$T	&Polarisation\\
		\middlehline
		I1V&	183.31$\pm$7.00    & 2.0 			& 0.8 		& V\\
		I2V&	183.31$\pm$3.40    & 1.5 			& 0.8 		& V\\
		I3V&	183.31$\pm$2.00    & 1.5 			& 0.8 		& V\\
		I4V&	243.20$\pm$2.50    & 3.0 			& 0.7 		& V\\
		I4H&	243.20$\pm$2.50    & 3.0 			& 0.7 		& H\\
		I5V&	325.15$\pm$9.50    & 3.0 			& 1.2 		& V\\
		I6V&	325.15$\pm$3.50    & 2.4 			& 1.3 		& V\\
		I6V&	325.15$\pm$1.50    & 1.6 			& 1.5 		& V\\
		I8V&	448.00$\pm$7.20    & 3.0 			& 1.4 		& V\\
		I9V&	448.00$\pm$3.00    & 2.0 			& 1.6 		& V\\
		I10V&	448.00$\pm$1.40    & 1.2 			& 2.0 		& V\\
		I11V&	664.00$\pm$4.20    & 5.0 			& 1.6 		& V\\
		I11H&	664.00$\pm$4.20    & 5.0 			& 1.6 		& H\\		
		\bottomhline
	\end{tabular}
	\begin{tabular}{lrrrr}
		\tophline
		Channel & Frequency 	& Bandwidth  	&NE$\Delta$T	&Polarisation\\
		\middlehline
		MWI-14&	183.31$\pm$7.00    & 2.0 			& 1.3 		& V\\
		MWI-15&	183.31$\pm$6.10    & 1.5 			& 1.2 		& V\\
		MWI-16&	183.31$\pm$4.90    & 1.5 			& 1.2 		& V\\
		MWI-16&	183.31$\pm$3.40    & 1.5 			& 1.2 		& V\\
		MWI-16&	183.31$\pm$2.00    & 1.5 			& 1.3 		& V\\	
		\bottomhline
	\end{tabular}
	\belowtable{} % Table Footnotes
\end{table*}
Ice Cloud Imager (ICI) is a new EPS-SG (EUMETSAT Polar System - Second Generation) sensor that will observe  Earth using submillimeter-wave (sub-mm) frequency range. The main objective of ICI is measure ice cloud properties and improve the representation of clouds in regional and global models. ICI is a conically scanning millimetre/sub-millimetre radiometer which will measure 13 frequencies from 183 GHz up to 664 GHz. Channels with centre frequencies 183.31, 325.15 and 448.0\,GHz are centered on water vapor absorption lines, and measure vertical polarization. While other channels around 243.0 and 664.0\,GHz are ``window channels'' and receive both vertical and horizontal polarization. 
In addition to ICI, the EPS-SG satellite will also have Microwave Imager (MWI) onboard. MWI will measure frequencies from 18.7 GHz up to 183\,GHz and provide data continuity to the existing microwave imager measurements. The common 183\,GHz channels among the two instruments shall allow cross-calibration between the two instruments. The channel configurations for ICI and MWI (only 183\,GHz) are provided in Table~\ref{tab:ICI_MWI_configuration}.

\subsection{ICI simulations}
\label{sec:arts_simulations}
%

**** Some parts copied directly from AWS report *****

@@

\section{Cloud correction in  183 GHz channels}
%
\subsection{Training data}
%
Out of the 200\,000 ICI and MWI channel simulations, 150\,000 cases are randomly picked to form the training set. The rest are used for testing. In the training set, 90\% of the data is randomly selected to form the training set, while the other 10\% form the \textit{testing-during-training} database. ARTS simulations are noise free, so to incorporate the satellite measurement uncertainties, gaussian noise is added to the input training data according to the channel NE$\Delta$T. The target training data is kept noise free. In order to build a robust learning network, random noise is added to the inputs at each training iteration. This exposes the model to a different datasets during the entire training process and avoids the memorisation of training samples. The input data is also normalized with mean and standard deviation.
It is assumed for the simulations that the ICI and MWI channels are mapped to a common footprint and resolution. In such case, remapping reduces the noise in MWI channels from 1.2\,K at 10\,Km resolution to 0.8\,K at 15\,Km resolution.
\subsection{Training}
%
%t
\begin{table}[t]
\label{tab:QRNN_models}	
\caption{Summary of the different QRNN models used in the study.}
\begin{tabular}{lll}
\tophline
QRNN model & Training inputs & Target \\
\middlehline
QRNN-simple & I1V, I5V, I6V, I7V, I8V, I9V, I10V, I11V 			 & I1V\\
			& I2V, I5V, I6V, I7V, I8V, I9V, I10V, I11V 			 & I2V\\
			& I3V, I5V, I6V, I7V, I8V, I9V, I10V, I11V 			 & I3V\\
			& MWI-15, I5V, I6V, I7V, I8V, I9V, I10V, I11V 		 & MWI-15\\	
			& MWI-16, I5V, I6V, I7V, I8V, I9V, I10V, I11V 		 & MWI-16\\
QRNN-all    & I1V, I2V, I3V, I5V, I6V, I7V, I8V, I9V, I10V, I11V & I1V\\	
			& I1V, I2V, I3V, I5V, I6V, I7V, I8V, I9V, I10V, I11V & I2V\\	
			& I1V, I2V, I3V, I5V, I6V, I7V, I8V, I9V, I10V, I11V & I3V\\

\bottomhline
\end{tabular}
\belowtable{} % Table Footnotes
\end{table}
To investigate the performance of training inputs, two QRNN models with different set of training inputs are analysed. In both models, the training set combines data from 183\,GHz, 325 GHz, 448\,GHz and 664\,GHz to predict cloud corrected observations for the target 183\,GHz channel.

In the first model, the training set includes the target 183\,GHz channel and the sub-mm channels. For example, to train for channel I1V, the input channels are I1V, I5V , I6V, I7V, I8V, I9V, I10V, I11V. A separate QRNN model is trained for each of the 183\,GHz channels. We shall refer this QRNN model as ``QRNN-simple''. In the second QRNN model, we suggest to use all three 183\,GHz channels (from ICI) concurrently, along with sub-mm channels. In this case, although the input training parameters are identical for all channels, the target channel is different and QRNN has to be trained separately for each. Further in text, we refer this model as ``QRNN-all''. Table~\ref{tab:QRNN_models} summarises the two QRNN models.

Apart from these two models, we also extend QRNN-simple to predict the clear-sky values for MWI channels. In this case, we combine the measurements from MWI-15(MWI-16) and the sub-mm channels to predict MWI-15(MWI-16). Since we assume that all channels are remapped to a common footprint, channels MWI-14, MWI-17 and MWI-18 are virtually identical to I1V, I2V and I3V, and thus results for them are not shown separately.

As described in section \ref{model_selection}, a grid search was implemented to select the best performing hyperparamters. The mean quantile loss and CRPS for different layer width and hidden layer configurations are shown in Fig\ref{fig:model_selection}. The results are for QRNN-simple with I3V as target channel. Increasing the complexity of the network by increasing the layer-width and depth has a positive impact on performance. However for four hidden layers, increasing the number of neurons beyond 128 has no significant impact on the performance. On basis of these results, a neural network with four hidden layers and 128 neurons in each layer was selected for QRNN-simple. For the optimising the training paramters, a customised  learning rate scheduler was implemented. The initial learning rate was reset after a certain number of epochs.  We started the training process with a initial learning rate of 0.1, and decreased it by a factor of 10 after 100 epochs. The best neural network performance was obtained when the network was trained three times with a new initial learning rate. For each training  if the validation loss remained unchanged till 6 training epochs, the learning rate was reduced by a factor of 2. We did not optimise the type of activation function and batch size. Rectified Linear Unit (ReLU) was used as the activation function  and the batch size was set to 128 samples for all QRNN models.

For QRNN-all a grid search (results not shown) over width and depth and learning rates resulted in similar performance, and an identical neural network was selected.

\begin{figure}[t]
	\centering
	\includegraphics[height=60mm]{Figures/CRPS.pdf} 
	\caption{CRPS(left) and mean quantile loss(right) for different combinations of layer width and hidden layers ($n_h$). The results are from QRNN-simple for channel I2V.}
	\label{fig:}	
\end{figure}

\subsection{Results}
%
%f 
\begin{figure}[t]
	\includegraphics[width=\textwidth]{Figures/PDF_predictions_ICI.pdf} 
	\caption{Distributions of predicted clear-sky values from QRNN-simple for channels I1V, I2V and I3V. }
	\label{fig:PDF_predictions}	
\end{figure}
%f 
\begin{figure}[t ]
	\includegraphics[width=\textwidth]{Figures/error_distribution_QRNN-single.pdf} 
	\caption{Error distributions for deviations of QRNN-simple predictions to clear-sky simulations for channels I1V, I2V and I3V. Label ``uncorrected'' represents the measurements, ``predicted'' denotes the entire dataset, while ``predicted(5\,K)'' refers to the dataset where cases with cloud correction greater than 5\,K are excluded.}
	\label{fig:error_distributions}	
\end{figure}

%t
\begin{table}[t]
	\caption{Bias, mean absolute error(MAE), standard deviation(STD), and measure of skewness(Skewness) for error distributions of predictions of I1V, I2V and I3V. Results from both QRNN-simple and QRNN-all are shown. The label ``All'' refers to the complete dataset, while in ``Filtered'', cases with cases with cloud correction greater than 5\,K(15\,K) are excluded from statistics. The fraction of cases removed by this filter are given in parentheses.}
	\label{tab:error_statistics_ici}
%	\tabcolsep=0.11cm
	\begin{tabular}{llrr|rrr|rrr}
		\tophline
		&&\multicolumn{2}{c|}{Simulations}& \multicolumn{3}{c|}{QRNN-simple} & \multicolumn{3}{c}{QRNN-all}\\
		\cline{3-10}
%		\hline
		&&   Clear-sky &   All-sky &   All &   Filtered(5K) & Filtered(15K) & All &   Filtered(5K) & Filtered(15K) \\
		\middlehline
%		\multicolumn{7}{c}{Channel - I1V}\\

Channel I1V &Bias     &   -0.00 &   -1.90&    -0.03 &      0.00(6.40\%) & 0.01(3.09\%)&-0.01 &0.01 (6.42\%)& 0.02(3.09\%) \\
			&MAE      &    0.64 &    2.35&     0.69 &      0.60 & 0.63  &  0.65 & 0.62& 0.60\\
			&STD      &    0.80 &    8.92&     1.05 &      0.78 &  0.84 &  0.97 & 0.84& 0.80\\
			&Skewness &   -0.01 &   -7.99&    -1.24 &     -0.44 & -0.48 & -0.36 &-0.51&-0.34\\
\middlehline
Channel I2V	&Bias     &   -0.00 &         -1.05 &    0.02 &      0.03(3.70\%)&0.02(1.60\%) &  0.02&   0.03(3.67\%)& 0.02(1.60\%)\\
			&MAE      &    0.64 &          1.54 &    0.56 &      0.50&  	  0.52 &  0.46&   0.42 &  0.52\\
			&STD      &    0.80 &          5.98 &    0.86 &      0.64&  	  0.69 &  0.70&   0.53 &  0.69\\
			&Skewness &    0.02 &        -10.64 &   -2.25 &     -0.22& 		 -0.58 & -1.69& -0.25 &-0.56\\
\middlehline	
Channel I3V &Bias     &   0.00  &         -0.63 &    0.02 &      0.02(2.18\%)&0.03(0.92\%)&	 0.04 &  0.04(2.18\%) & 0.04(0.92\%) \\
			&MAE      &   0.64  &          1.14 &    0.54 &      0.50		& 0.52&0.48 &    0.44 & 0.46\\
			&STD      &   0.80  &          4.26 &    0.80 &      0.64		& 0.68&0.71 &     0.56 & 0.60\\
			&Skewness &   0.00  &        -13.26 &   -1.40 &     -0.16		&-0.61&-1.41&   -0.11 & -0.77\\	
		\bottomhline
	\end{tabular}
	\belowtable{} % Table Footnotes
\end{table}

%t
\begin{table}[t]
	\caption{Same as Table~\ref{tab:error_statistics_ici}, but for channels MWI-15 and MWI-16. Results are from QRNN-simple.}
	\label{tab:statistics_mwi}
	\begin{tabular}{llrr|rrr}
		\tophline
		&&\multicolumn{2}{c|}{Simulations}& \multicolumn{3}{c}{QRNN-simple} \\
		\cline{3-7}
		%		\hline
		&&   Clear-sky &   All-sky &   		 All &   Filtered(5\,K) & Filtered(15\,K) \\
		\middlehline
 MWI-15 		&Bias     &    0.00 &         -1.19 &           -0.02 &                -0.01(4.41\%) & -0.02(1.87\%)\\
				&MAE      &    0.64 &          1.66 &            0.56 &                 0.49 		 &  0.52\\
				&STD      &    0.80 &          6.21 &            0.84 &                 0.64 		 &  0.69\\
				&Skewness &   -0.02 &         -9.87 &           -1.67 &                -0.29 		 & -0.47\\
		\middlehline
 MWI-16 		& Bias 	   &    0.00 &         -0.80 &           -0.04 &   -0.03(2.85\%) & -0.04(1.15\%)\\
				& MAE      &    0.64 &          1.31 &            0.54 &     0.49		 & 0.51\\
				& STD      &    0.80 &          5.01 &            0.82 &     0.63		 & 0.67\\
				& Skewness &    0.01 &        -12.04 &           -1.94 &    -0.23		 &-0.81\\
		\bottomhline			
	\end{tabular}
	\belowtable{} % Table Footnotes
\end{table}
QRNN predictions are estimates of the posterior distribution over different quantiles: $x_{\tau}$, for median, $\pm 1\sigma$, $\pm 2 \sigma$ and  $\pm 3 \sigma$ ($\tau$ = 0.002, 0.03, 0.16, 0.5, 0.84, 0.97, 0.998). To assess the accuracy of the predictions, the median of the posterior distribution is assumed to be the best estimate for the predicted clear-sky value. The prediction errors are calculated as the deviation of the predictions to their corresponding noise-free clear-sky values. We calculate the mean bias, mean absolute error and standard deviation of the errors. The asymmetry of error distributions around their mean is also calculated through the measure of skewness. In the next sections, we describe the performance of the two QRNN models for ICI and MWI channels.

\subsection{Prediction accuracy}
%
The distributions of median value of clear-sky predictions from QRNN-single are shown in Fig~\ref{fig:PDF_predictions}. The distributions of corresponding clear-sky simulations are also plotted as reference. The three figures correspond to channels: I1V, I2V and I3V. These results show that the clear-sky values predicted by QRNN-single have a very good match for the peak of the distributions, but a slight mismatch is evident towards the tails, where QRNN seems to predict slightly colder/warmer TBs.

For a quantitative evaluation of how accurate the predictions are, the  deviations of the median values to the clear-sky simulations are computed. Fig~\ref{fig:error_distributions} shows the error distributions of predictions for all three channels. The distribution of noise is also plotted for reference. The error metrics corresponding to these results are provided in Table~\ref{tab:error_statistics_ici}. Without any cloud impact, the error distributions should follow a Gaussian distribution, however the presence of clouds leads to a TB reduction, and introduces a high negative bias among the deviations. Among the three channels, the highest cloud impact is seen in channel I1V. The average bias in channel I1V measurements is -1.89\,K, however the QRNN-single predictions successfully reduces the average deviation to -0.03\,K. The predictions and the observations have a good agreement for the main peak of the distribution, albeit the prediction errors have a sharper peak and a larger spread.  The large spread is representative of the few cases which are either under/over predicted. If all the cases with correction greater than 5\,K are excluded, only a fraction of the total cases (6.42\%) are removed but the variability in predictions errors reduces significantly. This indicates that few cases with high cloud impact could be difficult to train and predict.

The performance of QRNN-single for I2V and I3V is analogous to I1V, though the accuracy seems to be higher for former. When all predictions are included, the average deviation for both I2V and I3V is -0.02\,K, but few cases with large errors increases the spread of the distributions. As observed for I1V, excluding cases with cloud correction greater than 5\,K removes the cases associated with low accuracy. Interestingly, the resulting spread of errors is also narrower than noise. After filtering, the error standard deviation for both I2V and I3V is 0.64\,K compared to 0.80\,K originating from measurement noise.

The results QRNN-all are also shown in Table~\ref{tab:error_statistics_ici}. Using additional information from other 183\,GHz channels has a definite positive impact on the QRNN training. A marked impact is seen for channel I1V, where the low measure of skewness over the entire test set indicates that the resulting distributions are more symmetric than QRNN-simple. When cases with correction greater than 5\,K are excluded, the variability of errors is smaller than noise. A similar trend is observed for channels I2V and I3V.

Table~\ref{tab:statistics_mwi} shows the metrics from error distributions for MWI-15 and MWI-16 predictions. Results from only QRNN-simple are shown. As shown above for ICI channels, the performance of QRNN-simple for the two MWI channels is consistent.

\subsection{Uncertainty quantification}
%
%f 
\begin{figure}[t]
	\includegraphics[width=\textwidth]{Figures/PDF_uncertainty_bins_QRNN-single.pdf}	
	\caption{Distribution of errors binned according to their uncertainty. Results are from QRNN-simple for channels I1V, I2V and I3V.}
	\label{fig:error_distribution_uncertainty_bins_I1V}	
\end{figure}
\begin{figure}[t]
	\includegraphics[height = 70mm]{Figures/calibration_QRNN_I2V.pdf}	
	\caption{Calibration of the prediction intervals obtained from QRNN-simple and QRNN-all for channel I2V. }
	\label{fig:calibration_I2V}	
\end{figure}
The biggest advantage of using QRNN is estimation of case-specific uncertainties. The quantiles can be used to construct a probability distribution of the predictions in contrast to other correction approaches which give out only point estimates. The predictions for each quantile can be used to construct the confidence intervals. The confidence interval for each point estimate quantifies it's uncertainty. For example, if $\tau_1$ and $\tau_2$ are two quantiles then there is $\tau_2-\tau_1$ probability that the true value will lie in between the range.
